### 2017-08-14 src/2_Finance.tex
avance cap 1

High frequency trades are short-term positions that commonly end the trading
day avoiding leaving opened positions to the next business day. HFT is
frequently associated to algorithm trading strategies, but the former is focused
in to reduce the market impact of large institutional positions and the later refers to trade execution strategies that are typically used by fund managers to buy or sell large amounts of assets. The duration of the positions in HFT it is not well-defined. Figure~\ref{fig:HFTtimes} shows a survey done to traders about the holding time
of a position opened. Most of them agreed that HFT refers to positions between
1-second and 10-minutes. Overnight positions are avoided since they are
riskier and also have more expensive fees, HFT firms end the trading day closing all
opened positions.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTtradestime}
  \caption{Holding time of an opened position of a high frequency trade.}
  \label{fig:HFTtimes}
\end{figure}
In 2014 HFT represented nearly 50\% of equity trades in the US and more than 20\%
in Europe showing a consistent fall since 2009 which was its best year. US market revenues
have fallen dramatically.
Figure~\ref{fig:HFTmarket} on the left shows HFT trades percentage of US and Europe equity shares. The right figure shows how revenues in US stocks have fallen the last years.

>>>>

High frequency trades are short-term positions that commonly end the trading day
avoiding leaving opened positions to the next business day. HFT is frequently
associated to algorithm trading strategies, but the former is focused into
reduce the market impact of large institutional positions and the later refers
to trade execution strategies that are typically used by fund managers to buy or
sell large amounts of assets. The duration of the positions in HFT it is not
well-defined. Figure~\ref{fig:HFTtimes} shows a survey done to traders about the
holding time of a position opened. Most of them agreed that HFT refers to
positions between 1-second and 10-minutes. Overnight positions are avoided since
they are riskier and also have more expensive fees, HFT firms end the trading
day closing all opened positions.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTtradestime}
  \caption{Holding time of an opened position of a high frequency trade.Source
  \cite{aldridge2009}}
  \label{fig:HFTtimes}
\end{figure}
In 2014 HFT represented nearly 50\% of equity trades in the US and more than
20\% in Europe showing a consistent fall since 2009 which was its best year. US
market revenues have fallen dramatically.  Figure~\ref{fig:HFTmarket} on the
left shows HFT trades percentage of US and Europe equity shares. The right
figure shows how revenues in US stocks have fallen the last years.
